Examining a Quarter Century of Publishing Trends in Social Work Research:

### 2015-09-29 manuscript.Rmd
adds boxplot

n.so.yr <- left_join(n.so, n.yr) %>%
    group_by(title) %>%
    summarise(first = min(year), last = max(year), n = n()) %>%
    arrange(desc(n)) %>%
    rename(Journal = title)

@@

>>>>

n.so.yr <- left_join(n.so, n.yr) %>%
    group_by(title) %>%
    summarise(first = min(year), last = max(year), n = n()) %>%
    arrange(desc(n)) %>%
    rename(Journal = title) %>%
    mutate(index="index_variable")

@@

```{r Figure 1 Boxplot of Article Counts}

ggplot(data=n.so.yr, aes(x=index, y=n)) +
  stat_boxplot(geom="errorbar")+
  geom_boxplot(outlier.size = 2)+
  ylab("Cumulative article count") +
  annotate("text", x = 0.87, y = 1600, label = "Families in Society")+
  annotate("text", x = 0.91, y = 1400, label = "Social Work") +
  annotate("text", x = 1.20, y = 1350, label = "British Journal of Social Work")+
  theme_bw()+
  theme(axis.title.x = element_blank()) +
  theme(panel.border = element_blank(), axis.line = element_line())+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
  scale_x_discrete(breaks=NULL)+
  theme(plot.title = element_text(size = 18))+
  theme(axis.text=element_text(size=10), axis.title=element_text(size=16))
